Exploring environmental impacts of colonial contacts on Indigenous communities in northeastern Taiwan

### 2024-08-25 analysis/paper/paper.qmd
minor edit

# Mateirals and Methods
To explore changes in resource use before and after the European arrival with associated long-distance trade, I examined zooarchaeological and botanical remains from 40 adjacent units at the major residential area excavated during the first season (2001-2004) at Kiwulan [@Chen2007]. The remains considered in this study are from dwelling spaces and trash pits that reflect daily dietary practices, whereas those from burials that might relate to ritual activities are excluded. These 40 units were selected because of their relatively intact archaeological contexts and spatial continuity, providing a consistent framework for understanding daily food practices over time on a settlement scale. Moreover, the same excavation and recovery methods applied at the site allow comparison between assembalges from different temporal sequences.

@@

<!-- Here's some example analysis code: -->

>>>>

# Mateirals and Methods
To explore changes in resource use before and after the European arrival with associated long-distance trade, I examined zooarchaeological and botanical remains from 40 adjacent units at the major residential area excavated during the first season (2001-2003) at Kiwulan [@Chen2007]. The remains considered in this study are from dwelling spaces and trash pits that reflect daily dietary practices, whereas those from burials that might relate to ritual activities are excluded. These 40 units were selected because of their relatively intact archaeological contexts and spatial continuity, providing a consistent framework for understanding daily food practices over time on a settlement scale. Moreover, the same excavation and recovery methods applied at the site allow comparison between assemblages from different temporal sequences.

@@
